Notation proposal

### 2011-05-31 analysis.tex
Fixed tex syntax error
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@780 ccdd05d5-56c1-461a-bf98-85f6876523b4
added intro paragraph and formatted to 80 columns
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@786 ccdd05d5-56c1-461a-bf98-85f6876523b4

Our method involves an offline planning stage and an online, low latency filtering stage.

@@

\subsubsection{Orthogonal \textsc{fir} filters

>>>>

In this section we describe an implementation of the method described in
section \ref{label{sec:method}} suitable for rapid gravitational-wave searches
for compact binary coalescence.  The previous method requires several
computations that can be done before the analysis is actually underway.  Thus
we divide the procedure into two stages 1) an offline planning stage and 2) an
online, low latency filtering stage.  The offline stage can be done before the
analysis is started an updated asychronously whereas the online stage must keep
up with the detector output and produce search results as rapidly as possible.
In the next two subsections we describe what these stages entail.

@@

\subsubsection{Orthogonal \textsc{fir} filters}
